% LaTeX document produced by pod2latex from "driver.pod".
% The followings need be defined in the preamble of this document:
%\def\C++{{\rm C\kern-.05em\raise.3ex\hbox{\footnotesize ++}}}
%\def\underscore{\leavevmode\kern.04em\vbox{\hrule width 0.4em height 0.3pt}}
%\setlength{\parindent}{0pt}

\section{DRIVER}%
\index{DRIVER}

\subsection*{NAME}\begin{verbatim}
  ___ _       _ _     __  __
 / __(_)_ __ | (_)_ _|  \/  |
| (_ | | '  \| | \ V / |\/| |
 \___|_|_|_|_|_|_|\_/|_|  |_|
\end{verbatim}

GimliVM --- interactive talker environment

\subsection*{SYNOPSIS}
driver {\tt [}options{\tt ]}

\subsection*{DESCRIPTION}
GimliVM opens up a predefined port allowing external 
connections to connect in its secure environment.  
Persons connected have a wide-varity of commands and 
options at their dispense, to better communicate with 
other connected persons.  Options and so forth can be 
tuned in the configuration file, which is listed in 
the MANIFEST and documentation.

\subsection*{OPTIONS}%
\index{OPTIONS}

\begin{description}

\item[-v, --verbose]%
\index{-v, --verbose@-v, --verbose}%
\hfil\\
Toggles the \$verbose program flag, producing extra
debugging output.

\item[-c, --config]%
\index{-c, --config@-c, --config}%
\hfil\\
You may exlcusively specifiy your configuration file
in the mannger of -c=$<$path$>$ or --config=$<$path$>$

\item[-p, --port]%
\index{-p, --port@-p, --port}%
\hfil\\
Setting this option with --port=$<$port number$>$ will
over-ride any pre-existing port varibles, including
from the configuration file.

\item[-f, --fork]%
\index{-f, --fork@-f, --fork}%
\hfil\\
Program will be forked off into the background.

\item[-q, --quit]%
\index{-q, --quit@-q, --quit}%
\hfil\\
Program executes in quiet mode, nothing will be
written to STDOUT

\end{description}

\subsection*{BUGS}
Millions upon millions, but none that I'm aware of.  Please send bug
reports to bugs@gimlivm.org

\subsection*{AUTHOR}
Douglas Richard Hanks, Jr. <$<$dhanks@resourcephoenix.com$>$>

\subsection*{COPYRIGHT}%
\index{COPYRIGHT}
\begin{verbatim}
 GimliVM - interactive talker environment
 Copyright (C) 2000  Douglas Richard Hanks, Jr.
\end{verbatim}
\begin{verbatim}
 This program is free software; you can redistribute it and/or modify
 it under the terms of the GNU General Public License as published by
 the Free Software Foundation; either version 2 of the License, or
 (at your option) any later version.
\end{verbatim}
\begin{verbatim}
 This program is distributed in the hope that it will be useful,
 but WITHOUT ANY WARRANTY; without even the implied warranty of
 MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
 GNU General Public License for more details.
\end{verbatim}
\begin{verbatim}
 You should have received a copy of the GNU General Public License
 along with this program; if not, write to the Free Software
 Foundation, Inc., 675 Mass Ave, Cambridge, MA 02139, USA.
\end{verbatim}

